Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
text

The classical approach to control synthesis has often disregarded
quantization as a minimal effect, thus proving unsound in the case of digital control systems.
Modern techniques focus on different elements of the discretization effect, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
the goal to either verify (e.g.~\cite{daes20161}) or optimise
(e.g.~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilisation as an invariant set that always converges toward the controllable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and binds their trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a `buffer' region for the safety specification.

>>>>

The classical approach to control synthesis has often disregarded quantization, 
thus resulting in general to unsound digital controllers. 
Modern techniques focus on different elements of discretization effects, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
with the goal either to verify (e.g.~\cite{daes20161}) or to optimise
(e.g.~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilisation as an invariant set that always converges toward the controllable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and bounds its trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a buffer region for the safety specification.
